Similar Article Detection Using Minhash Technique on Wikipedia\titlenote{This effort is part of the CMSC828G, Data Intensive Computing with MapReduce, class project.}

### 2013-04-21 article/sigproc-sp.tex
completed Related Work section

\section{Related Work}
Related work goes here...

>>>>

\section{Related Work}
A number of techniques have been implemented to identify similarity between documents in the literature. These techniques usually differ in terms of corpus of interest, signature representing the document, feature-set determined by the system, and the end goal. In addition to these differences, one can also consider the efficiency and scalability of the system, overall.

In this section, we will go over some of theses techniques offered in the literature. Additionally, we will highlight our novel contribution.

Broder et al. introduced shingling to compute document similarity and containment. They also presented methods for using a subset of shingles while still allowing similarity and containment computations \cite{broder:resemblance}.

Seo et al. defined a general framework for text reuse detection. They introduced Discrete Cosine Transform (DCT) fingerprinting for general or local text reuse detection with high accuracy and efficiency \cite{seo:dct}.

Zhang et al. presented partial duplicate detection algorithm using sequence matching that transforms partial-duplicate detection task into three MapReduce jobs: 1.Indexing, 2.Sequence Duplicate Detection, 3.Sequence Matching \cite{zhang:pdc}.

Hajishirzi et al. introduced an adaptive near-duplicate detection (ANDD) method by extending term-weighting framework to learn k-gram vectors. Provided that each document was represented by an informative real k-gram vector, similarity measures were computed to come up with predicted values of near-duplicates \cite{hajishirzi:andd}.

Lin described three MapReduce algorithms for computing pairwise similarity on document collections: 1.Based on brute force, 2.Treated as large-scale ad hoc retrieval, 3.Based on Cartesian product of postings lists \cite{lin:brute}.

Manku et al. used Charikar's fingerprinting technique for developing near-duplicate detection system. They presented an algorithmic technique for identifying existing f-bit fingerprints that differ from a given fingerprint in at most k bit-positions, for small k. They demonstrated that their system is useful not only for batch but also for online processing \cite{manku:web}.

Bendersky et al. examined two information flow representations: the timeline and the link graph. They proposed several simple unsupervised techniques for timeline construction link graph analysis \cite{bendersky:timeline}.

In order to handle large Wikipedia dumps with the order of tens or hundreds of gigabytes and even a few terabytes, we used MapReduce framework in this work, that was introduced by Dean and Ghemawat \cite{dean:mapreduce}. The implementation is able to stream the compressed bz2 dumps and feed into mappers and reducers for further processing, which will be detailed in the following sections.
